---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  font-family: Arial;
}
h2 {
  color: #0800FF;
}
```

# What's going on with this data?
## Instagram Ads Survey Insights and Analysis. 
1. This dynamic report tracks survey responses from an Instagram ads survey. The survey asks respondents three questions: 
- **Which type of products or services are on Instagram ads?**  
- **How relevant are the products on ads to the personal interests?**  
- **How many times have you seen the same ads?**  

2. Summary values (calculated in a code chunk below) include:  
- **Minimum count**   
- **Maximum count**   
- **Total count**   
- **Number of records**     

3. The report calculates key summary values for the number of times respondents have seen the same ads and creates two bar charts:  
- **One chart shows the frequency of responses for the type of the product ads**  
- **The other chart shows the frequency of  counts**   


```{r}
library(tidyverse)
google_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vS44M4hGnJWmtP5lR9MwR4CFErRXUqQUu2Zqga9JhcLOUNS_5_Q876kZCDUX6PhTcWbWtsgn5MAg0eN/pub?gid=904361660&single=true&output=csv"
logged_data <- read_csv(google_url)

logged_data_renamed <- logged_data %>%
  rename(ads_type = 2,
         ads_relevance = 3,
         ads_same_counts = 4)

min_counts <- round(min(logged_data_renamed$ads_same_counts), 1)
max_counts <- round(max(logged_data_renamed$ads_same_counts), 1)
total_counts <- round(sum(logged_data_renamed$ads_same_counts), 1)
num_counts <- length(logged_data_renamed$ads_same_counts)
print(paste("Minimum count:", min_counts))
print(paste("Maximum count:", max_counts))
print(paste("Total count:", total_counts))
print(paste("Number of records:", num_counts))

plot1 <- ggplot(logged_data_renamed, aes(x = factor(ads_type))) +
  geom_bar(fill = "blue") +
  labs(
    title = "Count of Ads by Ads Types",
    x = "Instagram Ads Types",
    y = "Counts"
  )
print(plot1)

# Bar Chart 2: Distribution of ads_same_counts responses
plot2 <- ggplot(logged_data_renamed, aes(x = factor(ads_same_counts))) +
  geom_bar(fill = "green") +
  labs(
    title = "Frequency of Same Ads Counts",
    x = "Same Ads Counts",
    y = "Counts"
  )
print(plot2)

```

[Dynamic Report is here](https://differndeeper.github.io/stats220/)
